Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-04 paper/ms.tex
update paper

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
			trend-filtered CDIPS light curves.} 
		Black points correspond to the minimum RMS across the available three
		aperture sizes.  
		The model (orange and gray lines) assumes aperture sizes reported 
		by \citet{Sullivan_et_al_2015}, and the effective area from 
		\citet{vanderspek_2018}.
		The noise from unresolved background stars (dotted gray line) is a function 
		of galactic latitude, and dominates over zodiacal light
		for faint stars near the galactic plane; the line shown assumes a
		sight-line towards the center of Sector 6, Camera 1 (further details
		are in \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\paragraph{ACF statistics}
TODO:
ACF statistics before and after detrending(?)

SNR of retrieved HJs?

Maybe movies of subtracted images?

Some stellar variability plots (perhaps of known stellar variables)?

Some focus on particular clusters?

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
			trend-filtered CDIPS light curves.} 
		Black points correspond to the minimum RMS across the available three
		aperture sizes.  
		The model (orange and gray lines) assumes aperture sizes reported 
		by \citet{Sullivan_et_al_2015}, and the effective area from 
		\citet{vanderspek_2018}.
		The noise from unresolved background stars (dotted gray line) is a function 
		of galactic latitude, and dominates over zodiacal light
		for faint stars near the galactic plane; the line shown assumes a
		sight-line towards the center of Sector 6, Camera 1 (further details
		are in \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{avg_acf.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{
    {\bf Percentiles of the average autocorrelation of
    $10^4$ randomly selected light curves from each sector.} The
    25$^{\rm th}$, 50$^{\rm th}$, and 75$^{\rm th}$ percentiles at
    time lags spaced by one hour are
    shown by dashed, solid, and dotted lines respectively.  The raw
    light curves (column name \texttt{IRM}) are shown in gray, and the
    TFA-detrended light curves are in black.
  \label{fig:avg_acf}
	}
\end{figure}

@@

\paragraph{ACF statistics}

The preceding discussion is only relevant to the white noise
properties of the light curves. 
In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
raw and TFA-filtered light curves.
The raw light curves have substantial systematic red noise; 
their average autocorrelation, evaluated at various time lags, is
positive.
The TFA-filtered light curves are much closer to gaussian~--~the
average autocorrelation between any two points in these light curves
is close to zero.
However, the average TFA-filtered light curve is not {\it exactly}
gaussian.
At time lags of a few hours or less, there is some excess power.
This suggests that additional detrending may be
necessary to maximize the effectiveness of planet searches (or the discovery of
any other signals via matched-filter techniques).
